RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-31 assets/illustration/ambient_backscatter_communication.tex
:bento: Update scattering paradigms

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [trapezium,minimum height=0.75cm,anchor=center] {};
	\node at (3,4.5) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (7,4) [rectangle,minimum size=1cm] {};
	\node at (10,0) [trapezium,rotate=180,minimum height=0.75cm,anchor=center] {};

	\node[draw=none] at (0,-0.75) {Legacy Transmitter};
	\node[draw=none] at (3,5) {Backscatter Reader};
	\node[draw=none] at (7,5) {Scattering Node};
	\node[draw=none] at (10,-0.75) {Legacy Receiver};

	\draw[loosely dashed,-latex] (1,0) -- (9,0);
	\draw[loosely dashed,-latex] (0,0.75) -- (2.5,4);
	\draw[loosely dashed,-latex] (0.75,0.5) -- (6.25,3.5);
	\draw[dashdotted,-latex] (6.25,4.5) -- (3.75,4.5);
	\draw[dashdotted,-latex] (7.75,4) -- (10,0.75);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (1.5,3.5) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (6.5,3) [rectangle,minimum size=1cm] {};
	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-1.375) {Legacy\\Transmitter};
	\node[draw=none] at (1,4.375) {Backscatter\\Reader};
	\node[draw=none] at (7,4.375) {Scattering\\Node};
	\node[draw=none] at (8,-1.375) {Legacy\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.25,1) -- (0.75,3);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (7.5,3) -- (8,1);

	\node[draw=none] at (4,0.35) {Modulated\\Signal};
	\node[draw=none] at (4,3.5) {Superimposed\\Signal};
\end{tikzpicture}

### 2022-08-31 assets/illustration/bistatic_backscatter_communication.tex
:bento: Update scattering paradigms

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (7,4) [rectangle,minimum size=1cm] {};
	\node at (10,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};

	\node[draw=none] at (0,-1.5) {Carrier Emitter};
	\node[draw=none] at (7,5) {Scattering Node};
	\node[draw=none] at (10,-1.5) {Backscatter Reader};

	\draw[-latex] (1,-1) -- (9.5,-1);
	\draw[-latex] (0.5,0) -- (6,4);
	\draw[loosely dotted,-latex] (8,4) -- (10,0.5);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (5,3) [rectangle,minimum size=1cm] {};
	\node at (8,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};

	\node[draw=none] at (0,-2) {Carrier\\Emitter};
	\node[draw=none] at (5,4.5) {Scattering\\Node};
	\node[draw=none] at (8,-2) {Backscatter\\Reader};

	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,3);
	\draw[decorate,decoration={snake,pre length=1cm,post length=1cm},-latex] (6,3) -- (8,0.35);

	\node[draw=none] at (1.5,2.2) {Carrier};
	\node[draw=none] at (7.25,2.2) {1};
	\node[draw=none] at (6.55,3.1) {0};
	\node[draw=none] at (7.95,1.3) {0};
\end{tikzpicture}

### 2022-08-31 assets/illustration/riscatter.tex
:bento: Update scattering paradigms

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (7,4) [circle,minimum size=1cm] {};
	\node at (10,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-0.75) {Primary Transmitter};
	\node[draw=none] at (7,5) {RIScatter Node};
	\node[draw=none] at (10,-0.75) {Cooperative Receiver};
	\draw[loosely dashed,-latex] (0.75,0) -- (9.25,0);
	\draw[loosely dashed,-latex] (0.5,0.5) -- (6.25,4);
	\draw[dashdotted,-latex] (7.75,4) -- (10,1);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
	\node at (5,3) [circle,minimum size=1.25cm] {};
	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.5) {RIScatter\\Node};
	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4,0.875) {Modulated\\Signal};
	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
\end{tikzpicture}

### 2022-08-31 assets/illustration/symbiotic_radio.tex
:bento: Update illustration assets
:bento: Update scattering paradigms

\begin{tikzpicture}[every node/.style={draw}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (7,4) [circle,minimum size=1cm] {};
	\node at (10,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-0.75) {Primary Transmitter};
	\node[draw=none] at (7,5) {RIScatter Node};
	\node[draw=none] at (10,-0.75) {Cooperative Receiver};
	\draw[loosely dashed,-latex] (0.75,0) -- (9.25,0);
	\draw[loosely dashed,-latex] (0.5,0.5) -- (6.25,4);
	\draw[dashdotted,-latex] (7.75,4) -- (10,1);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
	\node at (5,3) [rectangle,minimum size=1cm] {};
	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.375) {Scattering\\Node};
	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4,0.875) {Modulated\\Signal};
	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
\end{tikzpicture}
